Algebraic File Synchronization: Adequacy and Completeness

### 2017-09-30 p2/ordering.tex
Clarifications, todo flags

Let the command to the left of $\cxynv$ in $T$ be $\czwmv$.
As $S$ is simple, we know $n\neq m$.
If $n\unrel m$, then from \cref{ax_separate_commute} we know we can swap the two commands
and get an equivalent sequence.

\newcommand{\indx}{\varphi}
Otherwise, either $n\descendant m$, or $m\descendant n$, and so from
\cref{connected_changes} we know that $S$ contains a command on all nodes
between $n$ and $m$, and therefore so does $T$.
Let these nodes be $n_0, n_1, \ldots, n_k$ where $n_0=n$ and $n_k=m$,
and where 
either $n_\indx=\parentf{n_{\indx+1}}$ for all $\indx$ between $1$ and $k-1$,
or $n_{\indx+1}=\parentf{n_\indx}$ for all $\indx$.
We assume that $n_\indx=\parentf{n_{\indx+1}}$ is true.

@@

TODO:
It follows from the algorithm that:
\begin{mycor}\label{lemma:neighbor}
If $U$ contains commands on both $n$ and $\parent(n)$, then
there is a simple $U'\equiv U$ in which they are next to each other.
\end{mycor}

TODO:
It follows from this that given a simple set,
we can simply assume that it has an order.
Accordingly, we will at times treat not only sequences as sets,
but simple sets as sequences.

>>>>

Let the command to the left of $\cxynv$ in $T$ be $\czwmv$.
As $S$ is simple, we know $n\neq m$.
If $n\unrel m$, then from \cref{ax_separate_commute} we know we can swap the two commands
and get an equivalent sequence.
We finish the proof by showing that $n\unrel m$ must hold, as
all other cases lead to contradiction.

\newcommand{\indx}{\varphi}
If $n\nunrel m$, then either $n\descendant m$, or $m\descendant n$, and so from
\cref{connected_changes} we know that $S$ contains a command on all nodes
between $n$ and $m$, and therefore so does $T$.
Let these nodes be $n_0, n_1, \ldots, n_k$ where $n_0=n$ and $n_k=m$,
and where 
either $n_\indx=\parentf{n_{\indx+1}}$ for all $\indx$ between $1$ and $k-1$,
or $n_{\indx+1}=\parentf{n_\indx}$ for all $\indx$.
We assume that $n_\indx=\parentf{n_{\indx+1}}$ is true.

@@

TODO TODO TODO -- ONLY USED ONCE WHERE INTERNALS OF OLD PROOF ARE USED
\begin{mycor}\label{lemma:neighbor}
If a simple sequence $S$ contains commands on both $n$ and $\parent(n)$, then
there is a simple $S'\equiv S$ in which they are next to each other.
\end{mycor}

TODO TODO TODO:
It follows from this that given a simple set,
we can simply assume that it has an order.
Accordingly, we will at times treat not only sequences as sets,
but simple sets as sequences.

### 2017-09-30 p2/rec-sound.tex
Clarifications, todo flags

In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
If $B$ has a command on $m$, then
from \cref{lemma:neighbor}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
When describing our ordering algorithm in \cref{ordering} we saw
that the command on the parent path determines whether a pair of commands
is a construction or destruction pair,
and that this, in turn, determines whether the command on the child path must
precede or follow the other command as otherwise the sequence would break all filesystems.
This argument holds for both $A$ and $B$, and so the command on $m$ must be on
the same side of the command on $n$ in both sequences.

>>>>

In these cases, either $m=\parent(n)$ or $n=\parent(m)$.
If $B$ has a command on $m$, then
-- TODO TODO TODO --
from \cref{lemma:neighbor}
we know that there is a $B'$ in $\orderset{B}$ where it is next to $\cxynv$ (also in $B$),
and from \cref{simple_reorder_equiv} we know that $B'\equiv B$.
When describing our ordering algorithm in \cref{ordering} we saw
that the command on the parent path determines whether a pair of commands
is a construction or destruction pair,
and that this, in turn, determines whether the command on the child path must
precede or follow the other command as otherwise the sequence would break all filesystems.
This argument holds for both $A$ and $B$, and so the command on $m$ must be on
the same side of the command on $n$ in both sequences.
